---
title: 'Lab 7: Multiple Linear Regression Intro'
author: "Shayan Kaveh"
date: "11/9/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore Penguins

Use `GGally::ggpairs()` to create a new pairs plot.

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple Linear Regression

We are going to try to understand (a bit better) the relationships between multiple predictor variables and an outcome, which is penguin body mass. 

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on flipper length and bill depth (bad idea... there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# call model by name to return only coefficients:
model_1

# more information on the coefficients and model:
summary(model_1)
```
If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average.

Adjust R-squared says that 75.96% of outcome variable defined by incoming???

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + + species + sex, 
              data = penguins)

summary(model_2)
```
# Let's visualize this

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```

### A couple ways to get & report MLR model outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame.

```{r}
penguin_model_2_coef <- tidy(model_2)

penguin_model_2_coef
```

The Gentoo coefficient would be `r penguin_model_2_coef$estimate[4]`. 


## Look at model diagnostics

Use the plot() function.

```{r}
plot(model_2)
```

## Report the model outputs in a summary table

Use modelsummary:
```{r}
modelsummary(model_2)
```

